---
title: "Assignment 1: R Markdown practice"
author: "Minsu Kang and Minsung Kim"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: yes
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    self_contained: yes
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: yes
    smart: trues
    dev: svg
  word_document:
    toc: no
geometry: margin=0.7in
fontsize: 8pt
documentclass: article
urlcolor: blue
---
# Section
 **Section 001** 

# Course Goals

 By the end of the course, students will be able to:
 
* Use [GitHub](www.github.com) for creating a reproducible research document.

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;-- My GitHub username is: *write_your_github_username_here_in_italic_letter*.

* Obtain, clean, transform, and visualize a dataset using the R programming language. 

* Interpret, and predict, dataset, trends using statistical inference and models.  

* Critically examine and interpret, statistical claims reported in mass media


# Including Code
## Running R code in a code chunk
```{r}
x <- 2+2
x+3

```
The output of first line of code is not printed out because it is assigned to a variable instead.

The second line of output is printed out instead, but this means that the calculated value has not been saved for future use. 

## Displaying Graphs
```{r}
ggplot2::qplot(data = iris, x =Sepal.Length, y = Sepal.Width)
```
